Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-06-22 ms.tex
also removed the Aeolus figure.

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. We detect no statistically significant phase variations with wavelength. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{e_1821_096_map.png}\\
\includegraphics[width=0.45\textwidth]{e_1821_120_map.png}
\hspace{0.2in}
\includegraphics[width=0.45\textwidth]{e_1821_126_map.png}
\caption{{\it Aeolus} maps of the light curves at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.}\label{fig:spotModel}
\end{centering}
\end{figure*}

>>>>

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. We detect no statistically significant phase variations with wavelength. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@
